On $K_2$-analogue of Serre problem for $\SL_4$

### 2018-09-24 paper.tex
Started rewriting stuff

\section{Preliminaries}
\begin{comment}
Our notation and conventions follows~\cite[\S~4]{Vav09}.
Let $\Phi$ be an irreducible root system with some fixed basis of simple roots $\Pi = \{\alpha_1, \ldots, \alpha_\ell\}$.
For a root $\alpha\in\Phi$ we denote by $m_i(\alpha)$ the $i$-th coefficient in the expansion of $\alpha$ in $\Pi$,
 i.\,e. $\alpha = \sum_{i=1}^n m_i(\alpha) \alpha_i$.

We denote by $\Phi^\vee$ the \emph{dual root system of $\Phi$} consisting of coroots $\alpha^\vee = 2\alpha/(\alpha, \alpha)$, $\alpha\in \Phi$.
As usual, $P(\Phi^\vee)$ denotes the lattice spanned by the \emph{fundamental weights $\varpi_i$},
 that are uniquely determined by relations $\langle\varpi_i, \alpha_j^\vee \rangle = (\varpi_i, \alpha_j) = \delta_{ij}.$ %TODO: Mistake?
\end{comment}

@@

\section{Overview of Tulenbayev's proof of $K_2$-analogue of Serre problem}
\subsection{$\sigma$-pairs}
Let $\Phi$ be a root system
\begin{lemma} \label{lem:3.1f} Let $A$ be a local ring then any element $\alpha \in \St(\Phi, A)$ can be presented as a product 
$ $

@@

Notice that for $\varpi \in P(\Phi^\vee)$ and $\beta \in \ZZ \Phi$ one has $(\varpi, \beta) \in \ZZ $.
Consequently, for $\varepsilon \in R^*$ and $\varpi \in P(\Phi^\vee)$ the formula $\chi_{\varpi, \varepsilon}(\beta) = \varepsilon ^ {(\varpi, \beta)}$
defines a character $\chi_{\varpi, \varepsilon} \in \Hom(\ZZ \Phi, R^*)$.

Consider the action of $H=\Hom(\ZZ \Phi, R^*)$ on the set of generators $\mathcal{X}_{\Phi, R}$ of the Steinberg group $\St(\Phi, R)$ given by
\begin{equation} \chi \cdot x_\alpha(\xi) = x_\alpha(\chi(\alpha) \cdot \xi),\ \chi \in H,\ \alpha\in \Phi,\ \xi \in R. \end{equation}
Since $\chi$ is a character, this action respects the set of Steinberg relations $\mathcal{R}_{\Phi, R}$ and therefore gives a well-defined action of $H$ on $\St(\Phi, R)$.

In the sequel we will be mostly interested in the following example.
\begin{example}
Let $A$ be a ring, denote by $R$ the ring $A[t, t^{-1}]$ of Laurent polynomials over $A$ and let $\alpha_i \in \Pi$ be a simple root.
Define automorphisms $\beta_i^+$ and $\beta_i^-$ of $\St(\Phi, R)$ via $\beta_i^+ = \chi_{\varpi_i, t}$, $\beta_i^- = \chi_{\varpi_i, t^{-1}}$.
It is easy to see that
\begin{equation}\label{eq:sigma_act} \beta_i^\pm(x_\alpha(\xi)) = x_\alpha(t^{\pm m_i(\alpha)} \cdot \xi).\end{equation}
\end{example}

>>>>

\section{Preliminaries}
\begin{comment}
Our notation and conventions follows~\cite[\S~4]{Vav09}.
Let $\Phi$ be an irreducible root system

 that are uniquely determined by relations $\langle\varpi_i, \alpha_j^\vee \rangle = (\varpi_i, \alpha_j) = \delta_{ij}.$ %TODO: Mistake?
\end{comment}

@@

\section{Tulenbaev's factorization theorem}
Let $\Phi$ be a root system with some fixed basis of simple roots $\Pi = \{\alpha_1, \ldots, \alpha_\ell\}$.
For a root $\alpha\in\Phi$ we denote by $m_i(\alpha)$ the $i$-th coefficient in the expansion of $\alpha$ in $\Pi$,
 i.\,e. $\alpha = \sum_{i=1}^n m_i(\alpha) \alpha_i$.

We denote by $\Phi^\vee$ the corresponding dual root system, which, by definition, consists of all coroots 
 $\alpha^\vee = \frac{2}{(\alpha, \alpha)} \alpha$, where $\alpha \in \Phi$.
We denote by $P(\Phi^\vee)$ the integral lattice spanned by the \emph{fundamental co-weights $\varpi^\vee_i$} (i.\,e. weights of the dual root system).
Recall that the co-weights $\varpi^\vee_i$ are uniquely determined by the property $(\varpi_i^\vee, \alpha_j) = \delta_{ij}$.

Notice that for $\varpi \in P(\Phi^\vee)$ and $\beta \in \ZZ \Phi$ one has $(\varpi, \beta) \in \ZZ $.
Thus, for $\varepsilon \in R^*$ and $\varpi \in P(\Phi^\vee)$ we can define a character $\chi_{\varpi, \varepsilon} \in \Hom(\ZZ \Phi, R^*)$
 via the formula $\chi_{\varpi, \varepsilon}(\beta) = \varepsilon ^ {(\varpi, \beta)}$.

Every character $\chi \in \Hom(\ZZ \Phi, R^*)$ acts on the set of generators $\mathcal{X}_{\Phi, R}$ of the Steinberg group $\St(\Phi, R)$ via
\begin{equation} \chi \cdot x_\alpha(\xi) = x_\alpha(\chi(\alpha) \cdot \xi),\ \chi \in H,\ \alpha\in \Phi,\ \xi \in R. \end{equation}
It is not hard to check that the above formula gives a well-defined automorphism of $\St(\Phi, R)$ which we also denote by $\chi$.

\begin{example}
Let $A$ be a ring, denote by $R$ the ring $A[t, t^{-1}]$ of Laurent polynomials over $A$ and let $\alpha_i \in \Pi$ be a simple root.
Define automorphisms $\beta_i^+$ and $\beta_i^-$ of $\St(\Phi, R)$ via $\beta_i^+ = \chi_{\varpi_i, t}$, $\beta_i^- = \chi_{\varpi_i, t^{-1}}$.
It is easy to see that
\begin{equation}\label{eq:sigma_act} \beta_i^\pm(x_\alpha(\xi)) = x_\alpha(t^{\pm m_i(\alpha)} \cdot \xi).\end{equation}
\end{example}

\subsection{$\sigma$-pairs}

\begin{lemma} \label{lem:3.1f} Let $A$ be a local ring then any element $\alpha \in \St(\Phi, A)$ can be presented as a product 
$ $

@@
